---
title: 'Homework #1'
author: "Suguru Iwashiro"
date: "2022-08-31"
output: github_document
---

```{r setup, include=FALSE}
library(data.table)
library(ggplot2)
library(tidyverse)
library(DT)
library(dplyr)
library(tidyverse)
options(dplyr.summarise.inform = FALSE)
# Homework 3
roll20 <-c(6,1,3,1,6,1,6,5,1,3,4,1,3,4,6,1,1,6,1,1,4)
roll20 %in% 6

# Homework 4
x <- 1:50
w <- 1 + sqrt(x)/2
example1 <- data.frame(x=x, y= x + rnorm(x)*w)
attach(example1)

fm <- lm(y ~ x)
summary(fm)
lrf <- lowess(x, y)
plot(x, y)
lines(x, lrf$y)
abline(0, 1, lty=3)
abline(coef(fm))
detach()

rm(list = ls(all = TRUE)) 

load("/Users/Suguru/Desktop/Econometrics/Homework/HW1/Household_Pulse_data.RData")

Household_Pulse_data[1:10,1:7]
attach(Household_Pulse_data)
summary(TBIRTH_YEAR[GENID_DESCRIBE == "female"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "transgender"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "other"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "NA"])

mean(TBIRTH_YEAR[GENID_DESCRIBE == "female"])
sd(TBIRTH_YEAR[GENID_DESCRIBE == "female"])

mean(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
sd(TBIRTH_YEAR[GENID_DESCRIBE == "male"])

race_anywork <- Household_Pulse_data %>% group_by(RRACE,ANYWORK)%>% summarise(n = n())
race_anywork

white <- race_anywork[race_anywork$RRACE == "White",]
white_pro<-data.frame(prop.table(white$n))
rownames(white_pro) <- c("NA","Emp","Umemp")
white_pro

black<- race_anywork[race_anywork$RRACE == "Black",]
black_pro<-data.frame(prop.table(black$n))
rownames(black_pro) <- c("NA","Emp","Umemp")
black_pro

asian<- race_anywork[race_anywork$RRACE == "Asian",]
asian_pro <- data.frame(prop.table(asian$n))
rownames(asian_pro) <- c("NA","Emp","Umemp")
asian_pro

other<- race_anywork[race_anywork$RRACE == "Other",]
other_pro <- data.frame(prop.table(other$n))
rownames(other_pro) <- c("NA","Emp","Umemp")
other_pro
```

## 1. What are the names of the people in your study group?
John Robison, Safinaz Ali

## 3. Roll the dice 20 times and check that the result was a 6 or not.
Here is the result of rolling the dice 20 times
```{r}
roll20 <-c(6,1,3,1,6,1,6,5,1,3,4,1,3,4,6,1,1,6,1,1,4)
roll20 %in% 6
```

## 4.Replicate the commands given in the lecture notes R Basics for Lecture 1 to do some simple stats on the Household Pulse data. 

```{r}
x <- 1:50
w <- 1 + sqrt(x)/2
example1 <- data.frame(x=x, y= x + rnorm(x)*w)
attach(example1)

fm <- lm(y ~ x)
summary(fm)
lrf <- lowess(x, y)
plot(x, y)
lines(x, lrf$y)
abline(0, 1, lty=3)
abline(coef(fm))
detach()

rm(list = ls(all = TRUE)) 

load("/Users/Suguru/Desktop/Econometrics/Homework/HW1/Household_Pulse_data.RData")
Household_Pulse_data[1:10,1:7]

attach(Household_Pulse_data)
summary(TBIRTH_YEAR[GENID_DESCRIBE == "female"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "transgender"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "other"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "NA"])

mean(TBIRTH_YEAR[GENID_DESCRIBE == "female"])
sd(TBIRTH_YEAR[GENID_DESCRIBE == "female"])

mean(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
sd(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
```

I checked unemployment proportion by race. Asians had the highest employment rate(65.1%) during the pandemic.

```{r}
race_anywork <- Household_Pulse_data %>% group_by(RRACE,ANYWORK)%>% summarise(n = n())
race_anywork

white <- race_anywork[race_anywork$RRACE == "White",]
white_pro<-data.frame(prop.table(white$n))
rownames(white_pro) <- c("NA","Emp","Umemp")
white_pro

black<- race_anywork[race_anywork$RRACE == "Black",]
black_pro<-data.frame(prop.table(black$n))
rownames(black_pro) <- c("NA","Emp","Umemp")
black_pro

asian<- race_anywork[race_anywork$RRACE == "Asian",]
asian_pro <- data.frame(prop.table(asian$n))
rownames(asian_pro) <- c("NA","Emp","Umemp")
asian_pro

other<- race_anywork[race_anywork$RRACE == "Other",]
other_pro <- data.frame(prop.table(other$n))
rownames(other_pro) <- c("NA","Emp","Umemp")
other_pro
```

## 5.What you’re being asked to do.

I think this is a question about Binormal distribution and probability. It would be unfair or odd if the result was outside of the possibility rate based on the Confidence Intervals that were set up.
