---
title: 'Homework #1'
author: "Suguru Iwashiro"
date: "2022-08-28"
output: html_document
---

## 1. What are the names of the people in your study group?
John Robison, Safinaz Ali

## 3. Roll the dice 20 times and check that the result was a 6 or not.
```{r}
roll20 <-c(6,1,3,1,6,1,6,5,1,3,4,1,3,4,6,1,1,6,1,1,4)
roll20 == 6
```

## 4.Replicate the commands given in the lecture notes R Basics for Lecture 1 to do some simple stats on the Household Pulse data. 

```{r}
x <- 1:50
w <- 1 + sqrt(x)/2
example1 <- data.frame(x=x, y= x + rnorm(x)*w)
attach(example1)

fm <- lm(y ~ x)
summary(fm)
lrf <- lowess(x, y)
plot(x, y)
lines(x, lrf$y)
abline(0, 1, lty=3)
abline(coef(fm))
detach()

rm(list = ls(all = TRUE)) 
load("/Users/Suguru/Desktop/Econometrics/Homework/HW1/Household_Pulse_data.RData")
#glimpse(acs2017_ny) try this later
Household_Pulse_data[1:10,1:7]

attach(Household_Pulse_data)
summary(TBIRTH_YEAR[GENID_DESCRIBE == "female"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "transgender"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "other"])
summary(TBIRTH_YEAR[GENID_DESCRIBE == "NA"])

mean(TBIRTH_YEAR[GENID_DESCRIBE == "female"])
sd(TBIRTH_YEAR[GENID_DESCRIBE == "female"])

mean(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
sd(TBIRTH_YEAR[GENID_DESCRIBE == "male"])
```

I checked unemployed proportion by race. Asian stays high employed level.

```{r}
race_anywork <- Household_Pulse_data %>% group_by(RRACE,ANYWORK)
race_anywork
white <- race_anywork[race_anywork$RRACE == "White",]
white
white_pro <-prop.table(white$n)
white_pro
Black<- race_anywork[race_anywork$RRACE == "Black",]
Black
black_pro <- prop.table(Black$n)
black_pro
Asian<- race_anywork[race_anywork$RRACE == "Asian",]
Asian
Asian_pro <- prop.table(Asian$n)
Asian_pro
Other<- race_anywork[race_anywork$RRACE == "Other",]
Other
Other_pro <- prop.table(Other$n)
Other_pro
```

## 5.What you’re being asked to do.

Binormal distribution and expected value. It is unfair or cheating if the result was out of the possibility based on the Confidence Intervals you set up.
